Results

### 2021-02-12 reports/interactive-rbans.Rmd
Updates results

---
title: "Interactive report of the RBANS results"
author: "Lukáš 'hejtmy' Hejtmánek"
date: "25/03/2020"
output: 
  flexdashboard::flex_dashboard:
    vertical_layout: scroll
    orientation: rows
---
```{r setup, message=FALSE, warning=FALSE, results='hide', echo=FALSE}
library(plotly)
library(crosstalk)
library(knitr)
library(tidyverse)
knitr::opts_chunk$set(echo = FALSE)
opts_knit$set(root.dir = "../")

source("../functions/cdz-loading-pilot.R")
source("../functions/cdz-analysis.R")
source("../functions/cdz-helpers.R")
source("../functions/cdz-getters.R")
source("../functions/cdz-preprocess.R")
```

```{r loading}
df_ids <- get_sheet_ids()
df_demographics <- get_sheet_demographics()
df_sessions <- get_sheet_sessions()
df_rbans <- get_sheet_rbans()
```

```{r preprocessing}
df_rbans <- add_session_to_rbans(df_rbans, df_demographics)
df_rbans_long <- df_rbans %>%
    pivot_longer(-c(rbansid, trenink, diagnosis, first_training, session),
                 names_to = "subtest", values_to = "score")
df_rbans_long <- df_rbans_long %>%
  group_by(trenink, first_training, subtest) %>%
  summarise(group_avg = mean(score, na.rm = TRUE)) %>%
  ungroup() %>%
  right_join(df_rbans_long, by = c("trenink", "first_training", "subtest"))

df_rbans_long <- df_rbans_long %>%
  arrange(rbansid, session)

@@

```{r}
plot_ly(shared_rbans, x = ~session, y = ~scaled_score) %>%
  add_trace(type = "box",  color = ~as.factor(session),
            hoverinfo = "y", showlegend = TRUE, boxmean = TRUE) %>%
  layout(showlegend = FALSE, autosize = TRUE, height = 500)
```

@@

```{r}
plot_ly(shared_rbans, x = ~session, y = ~scaled_score) %>%
  add_trace(type = "scatter", x=~session, y = ~scaled_score,
            mode = "lines+markers", split = ~rbansid) %>%
  layout(showlegend = FALSE, autosize = TRUE, height = 500)
```

```{r eval = FALSE}
df_rbans_long %>%
  filter(subtest == "iq_celek") %>%
  filter(first_training == "TP") %>%
  plot_ly(x= ~session, y = ~scaled_score) %>%
   add_trace(type = "box",  color = ~as.factor(session),
            hoverinfo = "y", showlegend = TRUE, boxmean = TRUE) %>%
  add_trace(type = "scatter", y = ~scaled_score,
            mode = "lines+markers", split = ~rbansid) %>%
  layout(showlegend=FALSE)
````

>>>>

---
title: "Interactive report of the RBANS results"
author: "Lukáš 'hejtmy' Hejtmánek"
date: "`r Sys.Date()`"
output: 
  flexdashboard::flex_dashboard:
    vertical_layout: scroll
    orientation: rows
---
```{r setup, message=FALSE, warning=FALSE, results='hide', echo=FALSE}
library(plotly)
library(crosstalk)
library(knitr)
library(tidyverse)
knitr::opts_chunk$set(echo = FALSE)
#opts_knit$set(root.dir = "../")
```

```{r}
source("../functions/cdz-loading-pilot.R")
source("../functions/cdz-analysis.R")
source("../functions/cdz-helpers.R")
source("../functions/cdz-getters.R")
source("../functions/cdz-preprocess.R")
```

```{r loading}
df_results <- read.table("../run2-results-supermarket-sessions.csv", sep = ";",
                         header = TRUE)
df_demographics <- read.table("../demographics.csv", sep = ";", header = TRUE)
df_ids <- read.table("../information.csv", header = TRUE, sep = ";")
df_sessions <- read.table("../sessions.csv", header = TRUE, sep = ";")
df_rbans <- read.table("../rbans.csv", sep=";", header = TRUE) %>%
  add_session_to_rbans(df_demographics) %>%
  add_summaries_to_rbans()
```

```{r preprocessing}
df_rbans_long <- df_rbans %>%
    pivot_longer(-c(rbansid, trenink, diagnosis, first_training, session),
                 names_to = "subtest", values_to = "score")

df_rbans_long <- df_rbans_long %>%
  group_by(trenink, first_training, subtest) %>%
  summarise(group_avg = mean(score, na.rm = TRUE), .groups="drop") %>%
  right_join(df_rbans_long, by = c("trenink", "first_training", "subtest"))

df_rbans_long <- arrange(df_rbans_long, rbansid, session)
df_rbans_long <- mutate(df_rbans_long, fac_session = factor(session))

@@

```{r}
plot_ly(shared_rbans, x = ~session, y = ~scaled_score) %>%
  add_trace(type = "box",  color = ~fac_session,
            hoverinfo = "y", showlegend = TRUE, boxmean = TRUE) %>%
  layout(showlegend = FALSE, autosize = TRUE, height = 500)
```

@@

```{r}
plot_ly(shared_rbans, x = ~session, y = ~scaled_score) %>%
  add_trace(type = "scatter", x=~fac_session, y = ~scaled_score,
            mode = "lines", split = ~rbansid, color = ~rbansid) %>%
  add_markers(x = ~jitter(as.numeric(session), amount = 0.02), y = ~scaled_score, color = ~rbansid) %>%
  layout(showlegend = FALSE, autosize = TRUE, height = 500)
```

```{r eval = FALSE}
df_rbans_long %>%
  filter(subtest == "iq_celek") %>%
  filter(first_training == "TP") %>%
  plot_ly(x= ~fac_session, y = ~scaled_score) %>%
    add_trace(type = "box",  color = ~fac_session,
            hoverinfo = "y", showlegend = TRUE, boxmean = TRUE) %>%
    add_trace(type = "scatter", y = ~scaled_score,
              mode = "lines+markers", split = ~rbansid) %>%
    layout(showlegend=FALSE)
````

### 2021-02-12 reports/preprocessing-demographics.Rmd
Updates results

The final RBANS counts look like this
```{r rbansfinal}
df_rbans %>%
  group_by(rbansid) %>%
  summarise(n_sessions = sum(!is.na(testuceni)), .groups="drop") %>%
  count(n_sessions) %>%
  knitr::kable(col.names =  c("RBANS completed", "Number of subjects"))

@@

df_rbans %>%
  group_by(session) %>%
  summarise(n_sessions = sum(!is.na(testuceni))) %>%
  knitr::kable(col.names =  c("Session", "Number of subjects"))
```

>>>>

The final RBANS counts look like this
```{r rbansfinal, message=FALSE}
df_rbans %>%
  group_by(rbansid) %>%
  summarise(n_sessions = sum(!is.na(testuceni)), .groups="drop") %>%
  count(n_sessions) %>%
  knitr::kable(col.names =  c("RBANS completed", "Number of subjects"))

@@

df_rbans %>%
  group_by(session) %>%
  summarise(n_sessions = sum(!is.na(testuceni))) %>%
  knitr::kable(col.names =  c("Session", "Number of subjects"))

df_rbans %>%
  filter(session == 1) %>%
  group_by(first_training) %>%
  summarise(n_sessions = sum(!is.na(testuceni))) %>%
  knitr::kable(col.names =  c("First Training", "Number of subjects"))
```

### 2021-02-12 reports/results.Rmd
Updates results

```{r}

@@

Modelling the supermarket with mixed effect modelling gives us base trial difficulty of `r fixef(lmer_difficulty_session)[1]` and improvement of `r fixef(lmer_difficulty_session)[2 q]` per session. But it also models individual improvement and base performance. That is in the table below. Some participants have overall better base performance and some simply improve better or worse from this baseline. We can use these metrics to predict the RBANS performance change.

>>>>

@@

Modelling the supermarket with mixed effect modelling gives us base trial difficulty of `r fixef(lmer_difficulty_session)[1]` and improvement of `r fixef(lmer_difficulty_session)[2]` per session. But it also models individual improvement and base performance. That is in the table below. Some participants have overall better base performance and some simply improve better or worse from this baseline. We can use these metrics to predict the RBANS performance change.
